Solving Collective Spin Hamiltonians with Decoherence

### 2018-09-08 soc_squeezing/cumulant_expansions.tex
removed obsolete method for single-spin decoherence calculations
implemented and tested arbitrary single-weight collective-spin decoherence
relabeled some indices in general commutator

All collective spin Hamiltonians can be written in the form
\begin{align}
  H = \sum_{p,q,r} h_{pqr} S_+^p S_\z^q S_-^r,
  \label{eq:H_general}
\end{align}
where Hermiticity requires that $h_{pqr}=h_{rqp}$.  The Hamiltonian
for one-axis twisting with a transverse field, for example, is
\begin{align}
  H_{\t{TVF}}
  = \chi S_\z^2 + \Omega S_\x
  = \chi S_\z^2 + \f{\Omega}{2} S_+ + \f{\Omega}{2} S_-,
\end{align}
while the two-axis twisting Hamiltonians about $\p{\z,\y}$ and
$\p{\y,\x}$ are
\begin{align}
  H_{\t{TAT}}^{\z,\y}
  \propto S_\z^2 - S_\y^2
  = S_\z^2 + \f14 S_+^2 + \f14 S_-^2
  - \f12 S_+ S_- + \f12 S_\z,
\end{align}
and
\begin{align}
  H_{\t{TAT}}^{\y,\x}
  \propto S_\y^2 - S_\x^2
  = -\f12 S_+^2 - \f12 S_-^2.
\end{align}
The evolution of a general operator $S_+^\ell S_-^m S_\z^n$ under a
Hamiltonian of the form in \eqref{eq:H_general} is given by
\begin{align}
  \f{d}{dt} \p{S_+^\ell S_\z^m S_-^n}
  = i \sum_{p,q,r} h_{pqr}
  \sp{S_+^p S_\z^q S_-^r, S_+^\ell S_\z^m S_-^n}_-
  + \sum_\J \gamma_\J \D\p{\J;\O}
  \equiv \sum_{p,q,r} T^{\ell m n}_{pqr} S_+^p S_\z^q S_-^r,
  \label{eq:time_derivative}
\end{align}
where commutator and decoherence terms necessary for computing the
matrix elements $T^{\ell m n}_{pqr}$ of the time derivative operator
$d/dt$ are worked out Appendices \ref{sec:comm_general},
\ref{sec:decoherence_single}, and \ref{sec:decoherence_collective}.

@@

If all collective spin operators are written in the form
$S_\mu^\ell S_\z^m S_\bmu^n$ for $\bmu\equiv-\mu\in\set{+1,-1}$, then
the most general (anti-)commutator we need to consider is
\begin{align}
  \sp{S_\mu^p S_\z^a S_\bmu^q, S_\mu^r S_\z^b S_\bmu^s}_\pm
  = \S^{paq}_{rbs;\mu} \pm \S^{rbs}_{paq;\mu},
\end{align}
where
\begin{align}
  \S^{paq}_{rbs;\mu}
  \equiv S_\mu^p S_\z^a S_\bmu^q S_\mu^r S_\z^b S_\bmu^s
  = \sum_{k=0}^{\min\set{q,r}} k! { q \choose k } { r \choose k }
  S_\mu^{p+r-k} \tilde Z_{qrab;\mu}^{(k)} S_\bmu^{q+s-k},
\end{align}
and, in terms of $\xi_{qrk}^{(\ell)}$ as defined in \eqref{eq:xi_mnp},
\begin{align}
  \tilde Z_{qrab;\mu}^{(k)}
  &\equiv \p{\mu\sp{r-k}+S_\z}^a
  Z_{qr;\bmu}^{(k)} \p{\mu\sp{q-k}+S_\z}^b \\
  &= \sum_{\ell=0}^k \p{-1}^\ell \xi_{qrk}^{(\ell)}
  \sum_{m=0}^a \p{r-k}^{a-m} { a \choose m }
  \sum_{n=0}^b \p{q-k}^{b-n} { b \choose n }
  \mu^{a+b+\ell-m-n} S_\z^{\ell+m+n}.
\end{align}

@@

We first compute sums of single-spin operators sandwiching $S_\z^m$,
which will in turn be used to compute similar sums sandwiching
$S_\mu^\ell S_\z^m S_\bmu^n$.  The simplest case is
\begin{align}
  \sum_j \sigma_\z^{(j)} S_\z^m \sigma_\z^{(j)}
  = \sum_j \sigma_\z^{(j)} \sigma_\z^{(j)} S_\z^m
  = \sum_j \1_j S_\z^m
  = 2 S S_\z^m.
\end{align}
Similarly,
\begin{align}
  \sum_j \sigma_\z^{(j)} S_\z^m \sigma_\mu^{(j)}
  = S_\z^m \sum_j \sigma_\z^{(j)} \sigma_\mu^{(j)}
  = S_\z^m \sum_j \mu \sigma_\mu^{(j)}
  = \mu S_\z^m S_\mu
  = \mu S_\mu \p{\mu+S_\z}^m,
\end{align}
where in the last equality we used the identity derived in
\eqref{eq:push_z_mu_single} to push $S_\mu$ through $S_\z^m$.  Using
identity \eqref{eq:push_z_mu_Ss} to push $\sigma_\mu^{(j)}$ through
$S_\z^m$, we can also find
\begin{align}
  \sum_j \sigma_\mu^{(j)} S_\z^m \sigma_\mu^{(j)}
  = \sum_j \sigma_\mu^{(j)} \sigma_\mu^{(j)} \p{\mu+S_\z}^m
  = 0,
\end{align}
and
\begin{align}
  \sum_j \sigma_\bmu^{(j)} S_\z^m \sigma_\mu^{(j)}
  = \sum_j \sigma_\bmu^{(j)} \sigma_\mu^{(j)} \p{\mu+S_\z}^m
  = \p{S-\mu S_\z} \p{\mu+S_\z}^m.
\end{align}
We are now equipped to derive similar identities for general ordered
products of collective spin operators.  Making heavy use of identities
\eqref{eq:push_z_mu_sS} and \eqref{eq:push_mu_Ss} to push single-spin
operators through transverse collective-spin operators, we work
through all combinations that are unique up to Hermitian conjugation,
finding
\begin{align}
  \sum_j \sigma_\z^{(j)} S_\mu^\ell S_\z^m S_\bmu^n \sigma_\z^{(j)}
  &= 2\p{S-\ell-n} S_\mu^\ell S_\z^m S_\bmu^n
  + 4\ell n S_\mu^{\ell-1} \p{S+\mu S_\z}
  \p{-\mu+S_\z}^m S_\bmu^{n-1},
  \label{eq:san_z_z} \allowdisplaybreaks \\
  \sum_j \sigma_\z^{(j)} S_\mu^\ell S_\z^m S_\bmu^n \sigma_\mu^{(j)}
  &= \mu S_\mu^{\ell+1} \p{\mu+S_\z}^m S_\bmu^n
  + \mu n \p{-2S+2\ell+n-1} S_\mu^\ell S_\z^m S_\bmu^{n-1} \notag \\
  &\qquad - 2\mu\ell n\p{n-1} S_\mu^{\ell-1}
  \p{S+\mu S_\z} \p{-\mu+S_\z}^m S_\bmu^{n-2},
  \label{eq:san_z_mu} \allowdisplaybreaks \\
  \sum_j \sigma_\z^{(j)} S_\mu^\ell S_\z^m S_\bmu^n \sigma_\bmu^{(j)}
  &= -\mu S_\mu^\ell S_\z^m S_\bmu^{n+1}
  + 2\mu \ell S_\mu^{\ell-1} \p{S+\mu S_\z}\p{-\mu+S_\z}^m S_\bmu^n,
  \label{eq:san_z_bmu} \allowdisplaybreaks \\
  \sum_j \sigma_\mu^{(j)} S_\mu^\ell S_\z^m S_\bmu^n \sigma_\mu^{(j)}
  &= n S_\mu^{\ell+1} S_\z^m S_\bmu^{n-1}
  - n\p{n-1} S_\mu^\ell \p{S+\mu S_\z} \p{-\mu+S_\z}^m S_\bmu^{n-2},
  \label{eq:san_mu_mu} \allowdisplaybreaks \\
  \sum_j \sigma_\mu^{(j)} S_\mu^\ell S_\z^m S_\bmu^n \sigma_\bmu^{(j)}
  &= S_\mu^\ell \p{S+\mu S_\z}\p{-\mu+S_\z}^m S_\bmu^n,
  \label{eq:san_mu_bmu} \allowdisplaybreaks \\
  \sum_j \sigma_\bmu^{(j)} S_\mu^\ell S_\z^m S_\bmu^n \sigma_\mu^{(j)}
  &= S_\mu^\ell \p{S - \ell - n - \mu S_\z} \p{\mu + S_\z}^m S_\bmu^n
  + \ell n \p{2S - \ell - n + 2}
  S_\mu^{\ell-1} S_\z^m S_\bmu^{n-1} \notag \\
  &\qquad + \ell n \p{\ell-1} \p{n-1} S_\mu^{\ell-2} \p{S + \mu S_\z}
  \p{-\mu + S_\z}^m S_\bmu^{n-2}.
  \label{eq:san_bmu_mu}
\end{align}

@@

The effect of decoherence via single-spin dephasing is described by
\begin{align}
  \D\p{\sigma_\z/\sqrt2; \O}
  = \sum_j\p{\sigma_\z^{(j)} \O \sigma_\z^{(j)}
    - \f12\sp{\sigma_\z^{(j)} \sigma_\z^{(j)},\O}_+}
  = \f12 \sum_j \sigma_\z^{(j)} \O \sigma_\z^{(j)} - S \O,
\end{align}
where the factor $\sqrt2$ is inserted as
e.g.~$\D\p{\sigma_\z/\sqrt2;S_\mu}=-S_\mu$, such that the above
expression generates decay of single-weight transverse collective spin
operators at a unit rate.  From \eqref{eq:san_z_z}, we then have
\begin{align}
  \D\p{\sigma_\z/\sqrt2; S_\mu^\ell S_\z^m S_\bmu^n}
  = -\p{\ell+n} S_\mu^\ell S_\z^m S_\bmu^n
  + 2 \ell n S_\mu^{\ell-1} \p{S + \mu S_\z}
  \p{-\mu + S_\z}^m S_\bmu^{n-1}.
\end{align}
Decoherence via single-spin dephasing makes operators
$S_\mu^\ell S_\z^m S_\bmu^n$ ``grow'' in $S_\z$, although the sum
$\ell+m+n$ does not grow.

@@

The most general type of single-spin decoherence is described by
\begin{align}
  \D\p{\gamma;\O}
  = \sum_j\p{{\gamma^{(j)}}^\dag \O \gamma^{(j)}
    - \f12\sp{{\gamma^{(j)}}^\dag \gamma^{(j)}, \O}_+},
  &&
  \gamma \equiv \gamma_\z \sigma_\z
  + \gamma_+ \sigma_+ + \gamma_- \sigma_-.
  \label{eq:D_general_single}
\end{align}
To simplify \eqref{eq:D_general_single}, we expand
\begin{align}
  \gamma^\dag \O \gamma
  = \abs{\gamma_\z}^2 \sigma_\z \O \sigma_\z
  + \sum_\mu \p{\abs{\gamma_\mu}^2 \sigma_\bmu \O \sigma_\mu
    + \gamma_\bmu^* \gamma_\mu \sigma_\mu \O \sigma_\mu
    + \gamma_\z^* \gamma_\mu \sigma_\z \O \sigma_\mu
    + \gamma_\bmu^* \gamma_\z \sigma_\mu \O \sigma_\z},
\end{align}
and
\begin{align}
  \gamma^\dag \gamma
  = \abs{\gamma_\z}^2
  + \sum_\mu \sp{\abs{\gamma_\mu}^2 \f12 \p{1-\mu\sigma_\z}
    + \mu \p{\gamma_\z^*\gamma_\mu - \gamma_\bmu^*\gamma_\z}
    \sigma_\mu},
\end{align}
which implies
\begin{align}
  \D\p{\gamma;\O}
  &= \sum_{X\in\set{\z,+,-}} \abs{\gamma_X}^2 \D\p{\sigma_X;\O}
  + \sum_{\mu,j}
  \p{\gamma_\bmu^* \gamma_\mu \sigma_\mu^{(j)} \O \sigma_\mu^{(j)}
    + \gamma_\z^* \gamma_\mu \sigma_\z^{(j)} \O \sigma_\mu^{(j)}
    + \gamma_\bmu^* \gamma_\z \sigma_\mu^{(j)} \O \sigma_\z^{(j)}}
  \notag \\
  &\qquad -\f12 \sum_\mu \mu
  \p{\gamma_\z^*\gamma_\mu - \gamma_\bmu^*\gamma_\z} \sp{S_\mu, \O}_+.
\end{align}
In order to compute the effect of this decoherence on ordered products
of collective spin operators, we expand the anti-commutator
\begin{align}
  \sp{S_\mu, S_\mu^\ell S_\z^m S_\bmu^n}_+
  = S_\mu^{\ell+1} \sp{S_\z^m+\p{\mu+S_\z}^m} S_\bmu^n
  - n S_\mu^\ell \p{n-1+2\mu S_\z} S_\z^m S_\bmu^{n-1}.
\end{align}
Defining
\begin{align}
  \gamma_{\z,\mu}^{(\pm)}
  &\equiv \f12\p{\gamma_\z^* \gamma_\mu \pm \gamma_\bmu^* \gamma_\z},
  \allowdisplaybreaks \\
  K_{\ell mn;\mu}
  &\equiv S_\mu^\ell \p{S+\mu S_\z} \p{-\mu+S_\z}^m S_\bmu^n,
  \allowdisplaybreaks \\
  L_{\ell mn;\mu}^{(\gamma)}
  &\equiv \gamma_{\z,\mu}^{(+)} S_\mu^{\ell+1}
  \sp{\p{\mu+S_\z}^m-S_\z^m} S_\bmu^n
  + 2n \gamma_\bmu^* \gamma_z K_{\ell m,n-1;\mu}
  - 2\ell n\p{n-1} \gamma_z^* \gamma_\mu K_{\ell-1,m,n-2;\mu},
  \allowdisplaybreaks \\
  M_{\ell mn;\mu}^{(\gamma)}
  &\equiv \gamma_{\z,\mu}^{(-)} S_\mu^\ell
  S_\z^{m+1} S_\bmu^{n-1}
  -\mu \sp{\p{S-\ell-\f12n+\f12} \gamma_\z^* \gamma_\mu
    - \f12 \p{n-1} \gamma_{\z,\mu}^{(-)}}
  S_\mu^\ell S_\z^m S_\bmu^{n-1},
  \allowdisplaybreaks \\
  P_{\ell mn;\mu}
  &\equiv S_\mu^{\ell+1} S_\z^m S_\bmu^{n-1}
  - \p{n-1} K_{\ell m,n-2;\mu},
  \allowdisplaybreaks \\
  Q_{\ell mn;\mu}^{(\gamma)}
  &\equiv \mu L_{\ell mn;\mu}^{(\gamma)}
  + 2 n M_{\ell mn;\mu}^{(\gamma)}
  + n \gamma_\bmu^* \gamma_\mu P_{\ell mn;\mu},
\end{align}
we then have
\begin{align}
  \D\p{\gamma; S_\mu^\ell S_\z^m S_\bmu^n}
  = \sum_{X\in\set{\z,+,-}} \abs{\gamma_X}^2
  \D\p{\sigma_X; S_\mu^\ell S_\z^m S_\bmu^n}
  + Q_{\ell mn;\mu}^{(\gamma)} + \sp{Q_{nm\ell;\mu}^{(\gamma)}}^\dag.
\end{align}

@@

Defining

@@

  &= \mu \p{n-1} \sp{\p{\ell-n+\f12} \Gamma_{\z,\mu}^{(+)}

@@

  &\qquad + 2 \sp{\p{\ell-n+\f12} \Gamma_{\z,\mu}^{(+)}

@@

  &\qquad + 2\mu \Gamma_{\z,\mu}^{(-)} S_\mu^\ell S_\z^{m+2} S_\bmu^{n-1},

@@

  &\equiv \tilde L_{\ell mn;\mu}^{(\Gamma)}
  - n \tilde M_{\ell mn;\mu}^{(\Gamma)}
  + \Gamma_\bmu^* \Gamma_\mu \tilde P_{\ell mn;\mu},

>>>>

All collective spin Hamiltonians can be written in the form
\begin{align}
  H = \sum_{\ell,m,n} h_{\ell mn} S_+^\ell S_\z^m S_-^n,
  \label{eq:H_general}
\end{align}
where Hermiticity requires that $h_{\ell mn}=h_{nm\ell}$.  The
Hamiltonian for one-axis twisting with a transverse field, for
example, is
\begin{align}
  H_{\t{TVF}}
  = \chi S_\z^2 + \Omega S_\x
  = \chi S_\z^2 + \f{\Omega}{2} S_+ + \f{\Omega}{2} S_-,
\end{align}
while the two-axis twisting Hamiltonians about $\p{\z,\y}$ and
$\p{\y,\x}$ are
\begin{align}
  H_{\t{TAT}}^{\z,\y}
  \propto S_\z^2 - S_\y^2
  = S_\z^2 + \f14 S_+^2 + \f14 S_-^2
  - \f12 S_+ S_- + \f12 S_\z,
\end{align}
and
\begin{align}
  H_{\t{TAT}}^{\y,\x}
  \propto S_\y^2 - S_\x^2
  = -\f12 S_+^2 - \f12 S_-^2.
\end{align}
The evolution of a general operator $S_+^\ell S_-^m S_\z^n$ under a
Hamiltonian of the form in \eqref{eq:H_general} is given by
\begin{align}
  \f{d}{dt} \p{S_+^\ell S_\z^m S_-^n}
  = i \sum_{p,q,r} h_{pqr}
  \sp{S_+^p S_\z^q S_-^r, S_+^\ell S_\z^m S_-^n}_-
  + \sum_\J \gamma_\J \D\p{\J;\O}
  \equiv \sum_{p,q,r} T^{\ell m n}_{pqr} S_+^p S_\z^q S_-^r,
  \label{eq:time_derivative}
\end{align}
where commutator and decoherence terms necessary for computing the
matrix elements $T^{\ell m n}_{pqr}$ of the time derivative operator
$d/dt$ are worked out Appendices \ref{sec:comm_general},
\ref{sec:decoherence_single}, and \ref{sec:decoherence_collective}.

@@

If all collective spin operators are written in the form
$S_\mu^\ell S_\z^m S_\bmu^n$ for $\bmu\equiv-\mu\in\set{+1,-1}$, then
the most general (anti-)commutator we need to consider is
\begin{align}
  \sp{S_\mu^p S_\z^q S_\bmu^r, S_\mu^\ell S_\z^m S_\bmu^n}_\pm
  = \S^{pqr}_{\ell mn;\mu} \pm \S^{\ell mn}_{pqr;\mu},
\end{align}
where
\begin{align}
  \S^{pqr}_{\ell mn;\mu}
  \equiv S_\mu^p S_\z^q S_\bmu^r S_\mu^\ell S_\z^m S_\bmu^n
  = \sum_{k=0}^{\min\set{r,\ell}} k! { r \choose k } { \ell \choose k }
  S_\mu^{p+\ell-k} \tilde Z_{qr\ell m;\mu}^{(k)} S_\bmu^{r+n-k},
\end{align}
and, in terms of $\xi_{r\ell k}^{(a)}$ as defined in
\eqref{eq:xi_mnp},
\begin{align}
  \tilde Z_{qr\ell m;\mu}^{(k)}
  &\equiv \p{\mu\sp{\ell-k}+S_\z}^q
  Z_{r\ell;\bmu}^{(k)} \p{\mu\sp{r-k}+S_\z}^m \\
  &= \sum_{a=0}^k \p{-1}^a \xi_{r\ell k}^{(a)}
  \sum_{b=0}^q \p{\ell-k}^{q-b} { q \choose b }
  \sum_{c=0}^m \p{r-k}^{m-c} { m \choose c }
  \mu^{q+m+a-b-c} S_\z^{a+b+c}.
\end{align}

@@

We first compute sums of single-spin operators sandwiching $S_\z^m$,
which will in turn be used to compute similar sums sandwiching
$S_\mu^\ell S_\z^m S_\bmu^n$.  The simplest case is
\begin{align}
  \sum_j \sigma_\z^{(j)} S_\z^m \sigma_\z^{(j)}
  = \sum_j \sigma_\z^{(j)} \sigma_\z^{(j)} S_\z^m
  = \sum_j \1_j S_\z^m
  = 2 S S_\z^m.
\end{align}
Similarly,
\begin{align}
  \sum_j \sigma_\z^{(j)} S_\z^m \sigma_\mu^{(j)}
  = S_\z^m \sum_j \sigma_\z^{(j)} \sigma_\mu^{(j)}
  = S_\z^m \sum_j \mu \sigma_\mu^{(j)}
  = \mu S_\z^m S_\mu
  = \mu S_\mu \p{\mu+S_\z}^m,
\end{align}
where in the last equality we used the identity derived in
\eqref{eq:push_z_mu_single} to push $S_\mu$ through $S_\z^m$.  Using
identity \eqref{eq:push_z_mu_Ss} to push $\sigma_\mu^{(j)}$ through
$S_\z^m$, we can also find
\begin{align}
  \sum_j \sigma_\mu^{(j)} S_\z^m \sigma_\mu^{(j)}
  = \sum_j \sigma_\mu^{(j)} \sigma_\mu^{(j)} \p{\mu+S_\z}^m
  = 0,
\end{align}
and
\begin{align}
  \sum_j \sigma_\bmu^{(j)} S_\z^m \sigma_\mu^{(j)}
  = \sum_j \sigma_\bmu^{(j)} \sigma_\mu^{(j)} \p{\mu+S_\z}^m
  = \p{S-\mu S_\z} \p{\mu+S_\z}^m.
\end{align}
We are now equipped to derive similar identities for general ordered
products of collective spin operators.  Making (heavy) use of
identities \eqref{eq:push_z_mu_sS} and \eqref{eq:push_mu_Ss} to push
single-spin operators through transverse collective-spin operators, we
work through all combinations that are unique up to Hermitian
conjugation, finding
\begin{align}
  \sum_j \sigma_\z^{(j)} S_\mu^\ell S_\z^m S_\bmu^n \sigma_\z^{(j)}
  &= 2\p{S-\ell-n} S_\mu^\ell S_\z^m S_\bmu^n
  + 4\ell n S_\mu^{\ell-1} \p{S+\mu S_\z}
  \p{-\mu+S_\z}^m S_\bmu^{n-1},
  \label{eq:san_z_z} \allowdisplaybreaks \\
  \sum_j \sigma_\z^{(j)} S_\mu^\ell S_\z^m S_\bmu^n \sigma_\mu^{(j)}
  &= \mu S_\mu^{\ell+1} \p{\mu+S_\z}^m S_\bmu^n
  + \mu n \p{-2S+2\ell+n-1} S_\mu^\ell S_\z^m S_\bmu^{n-1} \notag \\
  &\qquad - 2\mu\ell n\p{n-1} S_\mu^{\ell-1}
  \p{S+\mu S_\z} \p{-\mu+S_\z}^m S_\bmu^{n-2},
  \label{eq:san_z_mu} \allowdisplaybreaks \\
  \sum_j \sigma_\z^{(j)} S_\mu^\ell S_\z^m S_\bmu^n \sigma_\bmu^{(j)}
  &= -\mu S_\mu^\ell S_\z^m S_\bmu^{n+1}
  + 2\mu \ell S_\mu^{\ell-1} \p{S+\mu S_\z}\p{-\mu+S_\z}^m S_\bmu^n,
  \label{eq:san_z_bmu} \allowdisplaybreaks \\
  \sum_j \sigma_\mu^{(j)} S_\mu^\ell S_\z^m S_\bmu^n \sigma_\mu^{(j)}
  &= n S_\mu^{\ell+1} S_\z^m S_\bmu^{n-1}
  - n\p{n-1} S_\mu^\ell \p{S+\mu S_\z} \p{-\mu+S_\z}^m S_\bmu^{n-2},
  \label{eq:san_mu_mu} \allowdisplaybreaks \\
  \sum_j \sigma_\mu^{(j)} S_\mu^\ell S_\z^m S_\bmu^n \sigma_\bmu^{(j)}
  &= S_\mu^\ell \p{S+\mu S_\z}\p{-\mu+S_\z}^m S_\bmu^n,
  \label{eq:san_mu_bmu} \allowdisplaybreaks \\
  \sum_j \sigma_\bmu^{(j)} S_\mu^\ell S_\z^m S_\bmu^n \sigma_\mu^{(j)}
  &= S_\mu^\ell \p{S - \ell - n - \mu S_\z} \p{\mu + S_\z}^m S_\bmu^n
  + \ell n \p{2S - \ell - n + 2}
  S_\mu^{\ell-1} S_\z^m S_\bmu^{n-1} \notag \\
  &\qquad + \ell n \p{\ell-1} \p{n-1} S_\mu^{\ell-2} \p{S + \mu S_\z}
  \p{-\mu + S_\z}^m S_\bmu^{n-2}.
  \label{eq:san_bmu_mu}
\end{align}

@@

The effect of decoherence via single-spin dephasing is described by
\begin{align}
  \D\p{\sigma_\z/\sqrt2; \O}
  = \f12 \sum_j\p{\sigma_\z^{(j)} \O \sigma_\z^{(j)}
    - \f12\sp{\sigma_\z^{(j)} \sigma_\z^{(j)},\O}_+}
  = \f12 \sum_j \sigma_\z^{(j)} \O \sigma_\z^{(j)} - S \O,
\end{align}
where the factor $\sqrt2$ is inserted as
e.g.~$\D\p{\sigma_\z/\sqrt2;S_\mu}=-S_\mu$, such that the above
expression generates decay of single-weight transverse collective spin
operators at a unit rate.  From \eqref{eq:san_z_z}, we then have
\begin{align}
  \D\p{\sigma_\z/\sqrt2; S_\mu^\ell S_\z^m S_\bmu^n}
  = -\p{\ell+n} S_\mu^\ell S_\z^m S_\bmu^n
  + 2 \ell n S_\mu^{\ell-1} \p{S + \mu S_\z}
  \p{-\mu + S_\z}^m S_\bmu^{n-1}.
\end{align}
Decoherence via single-spin dephasing makes operators
$S_\mu^\ell S_\z^m S_\bmu^n$ ``grow'' in $S_\z$, although the sum
$\ell+m+n$ does not grow.

@@

The most general type of single-spin decoherence is described by
\begin{align}
  \D\p{\gamma;\O}
  = \sum_j\p{{\gamma^{(j)}}^\dag \O \gamma^{(j)}
    - \f12\sp{{\gamma^{(j)}}^\dag \gamma^{(j)}, \O}_+},
  &&
  \gamma \equiv \gamma_\z \sigma_\z
  + \gamma_+ \sigma_+ + \gamma_- \sigma_-.
  \label{eq:D_general_single}
\end{align}
To simplify \eqref{eq:D_general_single}, we expand
\begin{align}
  \gamma^\dag \O \gamma
  = \abs{\gamma_\z}^2 \sigma_\z \O \sigma_\z
  + \sum_\mu \p{\abs{\gamma_\mu}^2 \sigma_\bmu \O \sigma_\mu
    + \gamma_\bmu^* \gamma_\mu \sigma_\mu \O \sigma_\mu
    + \gamma_\z^* \gamma_\mu \sigma_\z \O \sigma_\mu
    + \gamma_\bmu^* \gamma_\z \sigma_\mu \O \sigma_\z},
\end{align}
and
\begin{align}
  \gamma^\dag \gamma
  = \abs{\gamma_\z}^2
  + \sum_\mu \sp{\abs{\gamma_\mu}^2 \f12 \p{1-\mu\sigma_\z}
    + \mu \p{\gamma_\z^*\gamma_\mu - \gamma_\bmu^*\gamma_\z}
    \sigma_\mu},
\end{align}
which implies
\begin{align}
  \D\p{\gamma;\O}
  &= \sum_{X\in\set{\z,+,-}} \abs{\gamma_X}^2 \D\p{\sigma_X;\O}
  + \sum_{\mu,j}
  \p{\gamma_\bmu^* \gamma_\mu \sigma_\mu^{(j)} \O \sigma_\mu^{(j)}
    + \gamma_\z^* \gamma_\mu \sigma_\z^{(j)} \O \sigma_\mu^{(j)}
    + \gamma_\bmu^* \gamma_\z \sigma_\mu^{(j)} \O \sigma_\z^{(j)}}
  \notag \\
  &\qquad -\f12 \sum_\mu \mu
  \p{\gamma_\z^*\gamma_\mu - \gamma_\bmu^*\gamma_\z} \sp{S_\mu, \O}_+.
\end{align}
In order to compute the effect of this decoherence on ordered products
of collective spin operators, we expand the anti-commutator
\begin{align}
  \sp{S_\mu, S_\mu^\ell S_\z^m S_\bmu^n}_+
  = S_\mu^{\ell+1} \sp{S_\z^m+\p{\mu+S_\z}^m} S_\bmu^n
  - n S_\mu^\ell \p{n-1+2\mu S_\z} S_\z^m S_\bmu^{n-1}.
  \label{eq:S_mu_acomm}
\end{align}
Recognizing a resemblance between \eqref{eq:S_mu_acomm} and
\eqref{eq:san_z_mu}, we can collect terms to simplify
\begin{align}
  \sum_j \sigma_\z^{(j)} S_\mu^\ell S_\z^m S_\bmu^n \sigma_\mu^{(j)}
  - \f{\mu}{2} \sp{S_\mu, S_\mu^\ell S_\z^m S_\bmu^n}_+
  = K_{\ell mn;\mu} + L_{\ell mn;\mu}
  \label{eq:dec_z_mu}
\end{align}
and likewise
\begin{align}
  \sum_j \sigma_\mu^{(j)} S_\mu^\ell S_\z^m S_\bmu^n \sigma_\z^{(j)}
  + \f{\mu}{2} \sp{S_\mu, S_\mu^\ell S_\z^m S_\bmu^n}_+
  = K_{\ell mn;\mu} + M_{\ell mn;\mu}
  \label{eq:dec_mu_z}
\end{align}
with
\begin{align}
  K_{\ell mn;\mu}
  &\equiv \f{\mu}{2} S_\mu^{\ell+1}
  \sp{\p{\mu+S_\z}^m-S_\z^m} S_\bmu^n, \\
  L_{\ell mn;\mu}
  &\equiv \mu n S_\mu^\ell \sp{-2S+2\ell+\f32\p{n-1}+\mu S_\z}
  S_\z^m S_\bmu^{n-1} \notag \\
  &\qquad - 2\mu\ell n\p{n-1} S_\mu^{\ell-1}
  \p{S+\mu S_\z} \p{-\mu+S_\z}^m S_\bmu^{n-2}, \\
  M_{\ell mn;\mu}
  &\equiv \mu n S_\mu^\ell \sp{2\p{S+\mu S_\z}\p{-\mu+S_\z}^m
    - \p{\f12\sp{n-1}+\mu S_\z} S_\z^m} S_\bmu^{n-1}.
\end{align}
Defining for completion
\begin{align}
  P_{\ell mn;\mu}
  \equiv \sum_j
  \sigma_\mu^{(j)} S_\mu^\ell S_\z^m S_\bmu^n \sigma_\mu^{(j)}
  = n S_\mu^{\ell+1} S_\z^m S_\bmu^{n-1}
  - n\p{n-1} S_\mu^\ell \p{S+\mu S_\z} \p{-\mu+S_\z}^m S_\bmu^{n-2},
\end{align}
and
\begin{align}
  Q_{\ell mn;\mu}^{(\gamma)}
  \equiv \gamma_\bmu^* \gamma_\mu P_{\ell mn;\mu}
  + \p{\gamma_\z^* \gamma_\mu + \gamma_\bmu^* \gamma_\z}
  K_{\ell mn;\mu}
  + \gamma_\z^* \gamma_\mu L_{\ell mn;\mu}
  + \gamma_\bmu^* \gamma_\z M_{\ell mn;\mu},
  \label{eq:Q_single}
\end{align}
we finally have
\begin{align}
  \D\p{\gamma; S_\mu^\ell S_\z^m S_\bmu^n}
  = \sum_{X\in\set{\z,+,-}} \abs{\gamma_X}^2
  \D\p{\sigma_X; S_\mu^\ell S_\z^m S_\bmu^n}
  + Q_{\ell mn;\mu}^{(\gamma)} + \sp{Q_{nm\ell;\mu}^{(\gamma)}}^\dag.
\end{align}

@@

Collecting terms and defining

@@

  &= -\mu n\p{n-1} \sp{\p{\ell-n+\f12} \Gamma_{\z,\mu}^{(+)}

@@

  &\qquad - 2n \sp{\p{\ell-n+\f12} \Gamma_{\z,\mu}^{(+)}

@@

  &\qquad - 2\mu n \Gamma_{\z,\mu}^{(-)}
  S_\mu^\ell S_\z^{m+2} S_\bmu^{n-1},

@@

  &\equiv \Gamma_\bmu^* \Gamma_\mu \tilde P_{\ell mn;\mu}
  + \tilde L_{\ell mn;\mu}^{(\Gamma)}
  + \tilde M_{\ell mn;\mu}^{(\Gamma)},
